### 2017-03-26 thesis/latex/thesis.tex
Thesis: small commit.

%% \usepackage{tocbibind}
%% \usepackage{tocloft}
\usepackage{xpatch}

@@

\begin{document}
%% \newcommand{\listequationsname}{List of Equations}
%% \newlistof{myequations}{equ}{\listequationsname}
%% \newcommand{\myequations}[1]{%
%% \addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}

%% \xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}

%% \tableofcontents
\listoffigures
\clearpage
%% \listofmyequations
%% \newpage

@@

%% Begin with a paper-like introduction which talks about:

%% \begin{itemize}
%% \item How dynein is a structure which turns chemical energy into motion
%% \item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
%% \item How it's weird that a cellular structure can generate directed motion
%% \item Other cool stuff - make dynein mysterious and cool.
%% \end{itemize}

%% Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it

>>>>

@@

\begin{document}

\tableofcontents
\listoffigures
\newpage

@@

Begin with a paper-like introduction which talks about:

\begin{itemize}
\item How dynein is a structure which turns chemical energy into motion
\item How dynein's variation in step size and directionality suggest a large diffusion component \cite{reck2006single}
\item How it's weird that a cellular structure can generate directed motion
\item Other cool stuff - make dynein mysterious and cool.
\end{itemize}

Tell a story about dynein! Present the project as a story -- we don't have knowledge abotu dynein, it's really weird, we want to get info about it
